---
title: "Sex Prediction Challenge (sexpred)"
subtitle: "Starting kit"
author: "Florent Chuffart & Magali Richard"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_document:
    toc: true
    toc_float: true
    toc_depth: 3
    number_sections: false
---

```{r label="header", echo=FALSE, eval=TRUE}
knitr::opts_chunk$set(collapse=TRUE, comment = "#>", fig.width=9, fig.height=6, eval=TRUE, echo=FALSE, results="hide")
```

# I. Overview

```{r child='overview.Rmd'}
```

Lecture des données data_learn

```{r}
d=readRDS("data_learn.rds")

head(d[,1:15])

table(d$sex,useNA = "ifany")
table(d$histology,useNA = "ifany")
table(d$sex,d$histology,useNA = "ifany")
table(d$tissue_status,useNA = "ifany")


#define sex as 0 or 1

s=as.numeric(d$sex=="M")

#Get gene names

gs=colnames(d)[13:1012]
g=gs[1]

layout(matrix(1:2, 1), respect = TRUE)
plot(d[[g]],s, main="sex~gene", xlab="gene", ylab="sex")

#P(Y=1|X)=logitinv(a+b.x)

m=glm(s~d[[g]], family=binomial(logit))
summary(m)$coefficients
#pv=summary(m)$coefficients[2,5]

logitinv=function(x) 1/(1+exp(-x))
x=min(d[[g]]):max(d[[g]])
lines(x,logitinv(m$coefficients[[1]]+m$coefficients[[2]]*x),col=2, lwd=2)
legend("bottomright","logit(Y)=b.x",col=2,lty=1,cex=0.6)

plot(d[[g]],s,main="sex~gene", xlab="gene", ylab="sex")

py1x=function(t,m){
  x=m$coefficients[[1]]+m$coefficients[[2]]*t
  1/(1+exp(-x))
}

arrows(d[[g]],s,d[[g]],py1x(d[[g]],m),
       col=adjustcolor(4,alpha.f=0.2),length=0.05,lwd=2)
legend("bottomright","1-P(Y|X",col=4,lty=1,cex=0.6)

#Fonction pour la pvaleur 

pvs=sapply(gs, function(g){
  print(g)
  m=
    glm(c(s,0,0,1,1)~c(d[[g]],0,max(d[,gs]),0max(d[,gs])
    ), family = binomial(logit))
  pv=summary(m)$coefficients[2,4]
  pv
})



```

# II. How to participate?

## Where to go? 

The challenge is hosted on the codalab platform: https://competitions.codalab.org/

To participate, you need to:

1- create an acount on the codalab platform

2- subscribe to the *sexpred* challenge

3- constitute teams (up to 4 people) and design a team coordinator on the platform

## How to start?

```{r child='evaluation.Rmd'}
```

# III. Submission (example)

```{r child='submission_script_sex.Rmd'}
```
```{r}
```

# IV. Report / Evaluation

## Report

The goal will be to predict the sex of patients in a gene expression dataset. 

You will use the codalab platform to evaluate your methods. 

The challenge will be open for a week on the platform.
You will work in teams of 3 or 4.

You will report by team. 
This report should consist of 3 parts, with:

**A) Statistical methods used**

*For instance* :

- Descriptive statistics (actors, number of NA, pretreatment...)
- Methods: Which function for linear model? (*e.g* lm, aov, rlm, glm, other...), Which model are your main models? ...

**B) Critical evaluation of the progression of the score**

*For instance* :
For critical variation in your leader board score:

- Evaluation of your model (e.g. number of parameters...)
- What is your score on codalab?
    
**C) Discussion and biological interpretation**

*For instance* :

- Pros and cons each method
- Biological meaning (gene expression correlations, tissues status...)

## Evaluation

You will be evaluated on the report you provide (hability to clearly explain your approach, the methods used and the evolution of your prediction score), the codalab leader board score **WILL NOT** be used as a metric to evaluate your score. 

# V. References 

[NCBI/GENE] https://www.ncbi.nlm.nih.gov/gene

[TCGA] Data are coming from the TCGA (The cancer genome atlas). 
They were extracted from several cohorts of patients. 
Here are TCGA Study Abbreviations corresponding to each cancer. 
https://gdc.cancer.gov/resources-tcga-users/tcga-code-tables/tcga-study-abbreviations

[Codalab] https://competitions.codalab.org

[R] https://cran.r-project.org

[RStudio] https://www.rstudio.com

# Session Information

```{r, results="verbatim"}
sessionInfo()
```
