---
title: "Submission script"
output:
  html_document:
    number_sections: true
    toc: true
    toc_depth: 2
params:
  package_repository: "https://cloud.r-project.org"
  install_dependencies: true
---

# Package dependencies
- zip : to generate the zip files that contain the programs or the results to submit to the Codalab platform.

```{r label = "Submission - dependencies", include = FALSE}
if ( !exists(x = "params") ) {
    params                      <- NULL
}
if ( is.null(x = params$package_repository) ) {
    params$package_repository   <- "https://cloud.r-project.org"
}
if ( is.null(x = params$install_dependencies) ) {
    params$install_dependencies <- TRUE
}
print(params)
if ( params$install_dependencies ) {
    installed_packages <- installed.packages( )
    for (package in c("zip") ) {
        if ( !{ package %in% installed_packages } ) {
            print(x = paste("Installation of ", package, sep = "") )
            install.packages(
                pkgs = package
              , repos = params$package_repository
            )
        } else {
            print(x = paste(package, " is installed.", sep = "") )
        }
    }
    remove(list = c("installed_packages", "package") )
}
```


# Format of the submission

**For a code submission** : you have to make a zip file (no constrain on the namefile) that contains :
  - the file `metadata` that is generated by this script
  - your code inside a *R* file named `program.R`. This file will be sourced and have to contain :
    - a function `program` with `input` as argument : a matrix associated to your estimation.
  - any other files that you want to access from your function `program` : during the ingestion phase (when your code is evaluated), the working directory will be inside the directory obtained by unzipping your submission.

# Write a function to learn and predict the virulence

```{r label = "Submission - Program", echo = TRUE, results = "verbatim"}
#' The function to estimate the virulence
#'
#' @param input_learn a matrix to learn the model of virulence
#' @param input_test  a matrix on which we want to predict the virulence
#' @return the estimated virulence
#' @examples
#' program(input = d)
program <- function(input_learn, input_test) {
    ##
    ## YOUR CODE BEGINS HERE
    ##
    
    for ( v in c("sex", "tissue_status", "histology", "dead", "dead_at_24_months", "t", "n", "m", "tnm_stage") ) {
        input_learn[[ v ]] <- as.factor(x = input_learn[[ v ]])
    }
    ## summary(object = input_learn)

    ## We remove constant variables :
    idx <- apply(
        X      = input_learn,
        MARGIN = 2,
        FUN    = function(x) {
            length(x = table(x = x) ) > 1
        } )
    input_learn   <- input_learn[ , idx, drop = FALSE]

    ##
    ## YOUR CODE BEGINS HERE
    ##

    input_learn$os_months <- NULL
    input_learn$dead      <- NULL
    model <- glm(
        formula = dead_at_24_months ~ . ## sex + histology + t + n + m + tnm_stage
      , data    = input_learn
      , family  = binomial(link = 'logit')
    )
    ## summary(object = model)

    virulence_levels <- levels(x = input_learn$dead_at_24_months)

    pred <- predict.glm(object = model, newdata = input_test, type = "response")

    idx  <- pred <= 0.5
    pred[  idx ] <- virulence_levels[ 1 ]
    pred[ !idx ] <- virulence_levels[ 2 ]
    table(pred, useNA = "ifany")
    
    return( pred )
    
    ##
    ## YOUR CODE ENDS HERE
    ##
}
```


# Generate an estimation of the virulence (for test purpose)

```{r label = "Submission - Results", echo = TRUE, results = "verbatim"}
    ##
    ## DO NOT CHANGE THE FOLLOWING CODE
    ##

    data_learn <- readRDS(file = "data_learn.rds")

    ## we use the previously defined function 'program' to estimate A :
    res <- program(
        input_learn  = data_learn
        , input_test = data_learn ## we re-use 'data_learn' only for test purpose
    )
```


# Generate a zip file with the 'program' source code
    
```{r label = "Submission - program zip file", echo = TRUE, results = "verbatim"}
## we save the source code as a R file named 'program.R' :
dump(
    list = c("program")
  , file = "program.R"
)
## we also generate the 'metadata' file
cat(
    "command: Rscript $program/program.R $input $output"
  , file = "metadata"
)

## we create the associated zip file :
zip_program <- paste0("program_", format(x = Sys.time( ), format = "%Y_%m_%d_%S"), ".zip")
zip::zipr(
         zipfile = zip_program
       , files   = c("program.R", "metadata")
     )
print(x = zip_program)
```


# Submit the zip file

It generates the file *`r zip_program`*  for code submission.

Submit the zip submission file on the challenge in the tab `Participate`, menu `Submit / View Results` menu, sub-menu `Phase 1` or `Phase 2`, by clicking the `Submit` button after filling out some metadatas.

On the codalab challenge web page, The *STATUS* become : 
  - Submitting
  - Submitted	
  - Running
  - Finished

When it's finished :
  - You refresh the page and see your score
  - If enable, details for report could be downloaded by clicking *Download output from scoring step*.
  - Some logs are available to download.
  - Leader board is updated in the `Results` tab.


# Session Information

```{r, results="verbatim"}
sessionInfo( )
```
