---
title: "Histology Prediction Challenge (histpred)"
subtitle: "Starting kit"
author: "Florent Chuffart & Magali Richard"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_document:
    toc: true
    toc_float: true
    toc_depth: 3
    number_sections: false
---

```{r label="header", echo=FALSE, eval=TRUE}
knitr::opts_chunk$set(collapse=TRUE, comment = "#>", fig.width=9, fig.height=6, eval=TRUE, echo=FALSE, results="hide")
```

# I. Overview

```{r child='overview.Rmd'}
```

# II. How to participate?

## Where to go? 

The challenge is hosted on the codalab platform: https://competitions.codalab.org/

To participate, you need to:

1- create an acount on the codalab platform

2- subscribe to the *histpred* challenge


## How to start?

```{r child='evaluation.Rmd'}
```

# III. Submission (example)

```{r child='submission_script_histology.Rmd'}
```

# IV. Report / Evaluation

## Report

The goal will be to predict the histology of patients using gene expression dataset and clinical data. 

You will use the codalab platform to evaluate your methods. 

You will report your work in a html file (compiled using a .rmd file). Provide an URL containing your work in this [form](https://forms.gle/DrEg1b9pkhbe6jYf6).

Your report is due before December Tuesday 3rd.

## Evaluation

You will be evaluated on the report you provide (hability to clearly explain your approach, the methods used and the evolution of your prediction score), the codalab leader board score **WILL NOT** be used as a metric to evaluate your score. 

# V. References 

[NCBI/GENE] https://www.ncbi.nlm.nih.gov/gene

[TCGA] Data are coming from the TCGA (The cancer genome atlas). 
They were extracted from several cohorts of patients. 
Here are TCGA Study Abbreviations corresponding to each cancer. 
https://gdc.cancer.gov/resources-tcga-users/tcga-code-tables/tcga-study-abbreviations

[Codalab] https://competitions.codalab.org

[R] https://cran.r-project.org

[RStudio] https://www.rstudio.com

# Session Information

```{r, results="verbatim"}
sessionInfo()
```
